---
title: "bug_demo"
author: "Esa Turkulainen"
date: "1/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# echo "rmarkdown::render('forecast_script_FIN.Rmd', clean=TRUE,output_format='html_document',output_file='results/forecast_script_FIN_20201006.Rmd')" | R --slave

# Set working directory
ROOTDIR <- "~/blood_demand_forecast_NL/" # Your directory
DATADIR <- "~/production_forecasts/data/FACS"
HISTORYDIR <- "~/production_forecasts/histories/" # monthly
MONTHLYDIR <- paste0(HISTORYDIR, "monthly_") # monthly
WEEKLYDIR <- paste0(HISTORYDIR, "weekly_") # weekly

knitr::opts_chunk$set(root.dir = ROOTDIR, warning = FALSE, message = FALSE) # No warnings for final output
knitr::opts_knit$set(root.dir = ROOTDIR, warning = FALSE, message = FALSE)

# Colorblind palette
# black, orange, sky blue, green,
# yellow, blue, vermilion, purple
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
                "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# These colors work server side for now:
palette <- list(1, 1, 1, 0.7, "royalblue2", "deepskyblue1", "darkred", "darkgreen")
names(palette) <- c("alpha80", "alpha95", "alphaSeg", "alphaPred", "fill80", "fill95", "colPred", "colData")
```
```{r}
library(forecast)
library(ggplot2)
library(gridExtra)
library(knitr)
library(plyr)
library(lubridate)
library(numbers)
library(data.table)
library(R.utils)
library(DT)
library(stringr)
library(htmltools)
library(hash)
source("pffunctions.R")
# Set rolling window size in years
rw_years <- 3
start_date <- as.Date("2014-01-01")
```
```{r read_files, include = FALSE}
# Get all the files
files <- list.files(path = DATADIR, pattern = "FAC0091_*")  # Character vector of file names

# Compile a dataframe by going over all files
dlist <- list()
for (i in files) {
  # Read a single file to a df called d
  d <- read.delim(file = paste0(DATADIR, "/", i), header = FALSE, sep = ";", stringsAsFactors = FALSE, colClasses = 'character')
  
  if(length(d) == 26){
    d <- d[, !(names(d) %in% c("V10"))]  # The column numbers unfortunately vary between files, so we'll adjust
    }
  
  colnames(d) <- c("V1", "V2", "V3", "V4", "V5", "V6", "V7", "V8", "V9", "V10",
                   "V11", "V12", "V13", "V14", "V15", "V16", "V17", "V18", "V19", "V20",
                   "V21", "V22", "V23", "V24", "V25")  # This is done so as to have easier column handling later on
  dlist[[i]] <- d
}

d <- as.data.frame(rbindlist(dlist, fill = TRUE))
```

```{r modify_dataframe, include = FALSE}
# Divide into distributions (P) and returns (R)
P <- d[d$V1 == "P", ]
R <- d[d$V1 == "R", ]

# For distributions, we'll keep Distribution date, Quantity, ABO type, Volume, Exp date
keep <- c("V12", "V14", "V18", "V20", "V22", "V24")
distr <- P[keep]
colnames(distr) <- c("date", "product", "quantity", "ABO", "volume", "exp")

# For returns we keep the return date and quantity
keep <- c("V4", "V5", "V7")
retrn <- R[keep]
colnames(retrn) <- c("date", "product", "quantity")

# Datify
distr$date <- dmy(distr$date); distr$exp <- dmy(distr$exp)
retrn$date <- dmy(retrn$date)

# Numerify
distr$quantity <- as.numeric(distr$quantity); distr$volume <- as.numeric(distr$volume)
retrn$quantity <- as.numeric(retrn$quantity)

# Product codes for red cell products
red.codes <- c("budTR001", "A0071V00", "A0074V00", "A0092VA0", "A0092VB0", 
               "E3844V00", "E3845V00", "E3846VA0", "E3846VB0", "E3846VC0",
               "E3846V00", "E3847VA0", "E3847VB0", "E3847VC0", "E3847V00",
               "E3936VA0", "E3936VB0", "E3939V00", "E3940V00", "E4683V00",
               "E7668V00", "E7673V00", "E4999V00", "E5000V00")

red.distr <- distr[distr$product %in% red.codes, ]
red.retrn <- retrn[retrn$product %in% red.codes, ]

# Product codes for platelets
plat.codes <- c("budTR002", "trEnnApu", "A0004V00", "A0005V00", "A0006V00", "A0007V00", "A0008V00",
                "A0086VA0", "A0086VB0", "A0086V00", "A0088V00", "A0088VA0", "A0088VB0", "A0089V00",
                "A0089VB0", "A0089VA0", "A0090V00", "A0090VA0", "A0090VB0", "A0018V00", "A0020V00", 
                "A0021V00", "A0021VA0", "A0021VB0", "A0047V00", "A0049V00", "A0051V00", "A0054V00",
                "A0055V00", "A0056V00", "A0057V00", "A0059V00", "A0060V00", "A0067VA0", "A0067VB0",
                "A0067V00", "A0068VA0", "A0068VB0", "A0068V00", "A0075V00", "A0101V00", "A0102V00",
                "E3949V00", "E3953V00", "E3954V00", "E3955V00", "E3956V00", "E3957V00", "E3958V00",
                "E3959V00", "E3960V00", "E3961V00", "E3962V00", "E3963V00", "E3964V00", "E3965V00", 
                "E3966V00", "E3968VA0", "E3968VB0", "E3968V00", "E3970V00", "E3971V00", "E3973V00",
                "E3974V00", "E3976V00", "E3981V00", "E3995V00", "E3996V00", "E3997V00", "E3997VA0",
                "E3997VB0", "E4002V00", "E4004V00", "E6782V00", "E6783V00", "E6953V00", "E6860V00",
                "E6874VA0", "E6874V00", "E6874VB0", "E6875VB0", "E6875V00", "E7530V00", "E7530VA0",
                "E7530VB0", "E7531V00", "E7531VA0", "E7531VB0", "E6875VA0")

plat.distr <- distr[distr$product %in% plat.codes, ]
plat.retrn <- retrn[retrn$product %in% plat.codes, ]
```


```{r create_datasets, include = FALSE}
# Create a full sequence of dates for imputation purposes
all.dates <- (seq.Date(min(red.distr$date),
                       max(red.distr$date),
                       "day"))
###           ###
#   RED CELLS   #
###           ###
all.red <- aggregate(red.distr$quantity, by = list(red.distr$date), sum); colnames(all.red) <- c("date", "pcs")
# Merge into a whole set with NAs
all.red <- merge(x = data.frame(date = all.dates),
                 y = all.red,
                 all.x = TRUE)
# Replace with zeroes
all.red[is.na(all.red)] <- 0
# Cut to time after 2014
all.red <- all.red[all.red$date >= start_date, ]

###           ###
#  RED RETURNS  #
###           ###

all.red.retrn <- aggregate(red.retrn$quantity, by = list(red.retrn$date), sum); colnames(all.red.retrn) <- c("date", "pcs")
# Merge into a whole set with NAs
all.red.retrn <- merge(x = data.frame(date = all.dates),
                 y = all.red.retrn,
                 all.x = TRUE)
# Replace with zeroes
all.red.retrn[is.na(all.red.retrn)] <- 0
# Cut to time after 2014
all.red.retrn <- all.red.retrn[all.red.retrn$date >= start_date, ]


# Extracting types
Ominus.distr <- extract_type(red.distr, "O -",start_date)  # This our custom function, see pffunctions.R
Oplus.distr <- extract_type(red.distr, "O +",start_date)
Aminus.distr <- extract_type(red.distr, "A -",start_date)
Aplus.distr <- extract_type(red.distr, "A +",start_date)
Bminus.distr <- extract_type(red.distr, "B -",start_date)
Bplus.distr <- extract_type(red.distr, "B +",start_date)
ABminus.distr <- extract_type(red.distr, "AB-",start_date)
ABplus.distr <- extract_type(red.distr, "AB+",start_date)


###           ###
#   PLATELETS   #
###           ###
all.plat <- aggregate(plat.distr$quantity, by = list(plat.distr$date), sum); colnames(all.plat) <- c("date", "pcs")
# Merge into a whole set with NAs
all.plat <- merge(x = data.frame(date = all.dates),
                  y = all.plat,
                  all.x = TRUE)
# Replace with zeroes
all.plat[is.na(all.plat)] <- 0
# Cut to time after 2014
all.plat <- all.plat[all.plat$date >= start_date, ]

###           ###
# PLAT RETURNS  #
###           ###
all.plat.retrn <- aggregate(plat.retrn$quantity, by = list(plat.retrn$date), sum); colnames(all.plat.retrn) <- c("date", "pcs")
# Merge into a whole set with NAs
all.plat.retrn <- merge(x = data.frame(date = all.dates),
                  y = all.plat.retrn,
                  all.x = TRUE)
# Replace with zeroes
all.plat.retrn[is.na(all.plat.retrn)] <- 0
# Cut to time after 2014
all.plat.retrn <- all.plat.retrn[all.plat.retrn$date >= start_date, ]
```

```{r datasets_monthly, include = FALSE, warning = FALSE}
# Aggregate all by months
red.monthly <- aggregate(pcs ~ month(date) + year(date), data = all.red, FUN = sum)
red.retrn.monthly <- aggregate(pcs ~ month(date) + year(date), data = all.red.retrn, FUN = sum)

Ominus.monthly <- aggregate(pcs ~ month(date) + year(date), data = Ominus.distr, FUN = sum)
Oplus.monthly <- aggregate(pcs ~ month(date) + year(date), data = Oplus.distr, FUN = sum)
Aminus.monthly <- aggregate(pcs ~ month(date) + year(date), data = Aminus.distr, FUN = sum)
Aplus.monthly <- aggregate(pcs ~ month(date) + year(date), data = Aplus.distr, FUN = sum)
Bminus.monthly <- aggregate(pcs ~ month(date) + year(date), data = Bminus.distr, FUN = sum)
Bplus.monthly <- aggregate(pcs ~ month(date) + year(date), data = Bplus.distr, FUN = sum)
ABminus.monthly <- aggregate(pcs ~ month(date) + year(date), data = ABminus.distr, FUN = sum)
ABplus.monthly <- aggregate(pcs ~ month(date) + year(date), data = ABplus.distr, FUN = sum)

plat.monthly <- aggregate(pcs ~ month(date) + year(date), data = all.plat, FUN = sum)
plat.retrn.monthly <- aggregate(pcs ~ month(date) + year(date), data = all.plat.retrn, FUN = sum)

# Dates
#months <- seq(from = as.Date("2009-01-01"), to = max(distr$date), by = "month")
months <- seq(from = start_date, to = max(distr$date), by = "month") #This needs to be tuned based on your data set

# Adjustment series
adj <- as.numeric(bizdays(ts(months, 
                             start = c(year(start_date), month(start_date), day(start_date)), #  c(year, month, day) is apparently the only robust way to do this.
                             frequency = 12), FinCenter = "Zurich"))

# scaler <- as.numeric(bizdays(ts(1, start = decimal_date(months[length(months)]), frequency = 12), FinCenter = "Zurich")) This was written to scale a singular forecasted month back to real values, for saving-to-file purposes

end_date <- months[length(months)] # Ugly but around 30 times faster than tail(x, 1)!
reverse_adj <- as.numeric(bizdays(ts(seq(23), 
                                     start = c(year(end_date), month(end_date), day(end_date)), 
                                     frequency = 12), FinCenter = "Zurich")) # This is the old implementation that used to be fed into the forecasting function. We'll now repurpose it so it can be used both for tabling and plotting.

# Create a master frame
monthly <- data.frame(date = months,
                      red = red.monthly$pcs/adj,
                      red.ret = red.retrn.monthly$pcs/adj,
                      red.sales = red.monthly$pcs/adj - red.retrn.monthly$pcs/adj,
                      Ominus = Ominus.monthly$pcs/adj,
                      Oplus = Oplus.monthly$pcs/adj,
                      Aminus = Aminus.monthly$pcs/adj,
                      Aplus = Aplus.monthly$pcs/adj,
                      Bminus = Bminus.monthly$pcs/adj,
                      Bplus = Bplus.monthly$pcs/adj,
                      ABminus = ABminus.monthly$pcs/adj,
                      ABplus = ABplus.monthly$pcs/adj,
                      plat = plat.monthly$pcs/adj,
                      plat.ret = plat.retrn.monthly$pcs/adj,
                      plat.sales = plat.monthly$pcs/adj - plat.retrn.monthly$pcs/adj)

monthly_real <- data.frame(date = months,
                           red = red.monthly$pcs,
                           red.ret = red.retrn.monthly$pcs,
                           red.sales = red.monthly$pcs - red.retrn.monthly$pcs,
                           Ominus = Ominus.monthly$pcs,
                           Oplus = Oplus.monthly$pcs,
                           Aminus = Aminus.monthly$pcs,
                           Aplus = Aplus.monthly$pcs,
                           Bminus = Bminus.monthly$pcs,
                           Bplus = Bplus.monthly$pcs,
                           ABminus = ABminus.monthly$pcs,
                           ABplus = ABplus.monthly$pcs,
                           plat = plat.monthly$pcs,
                           plat.ret = plat.retrn.monthly$pcs,
                           plat.sales = plat.monthly$pcs - plat.retrn.monthly$pcs)

beginning <- tail(monthly$date, ((rw_years + 1) * 12 + 1))[1] # Define beginning of (monthly) time here
end_date <- monthly$date[length(monthly$date)] # Not using "today()" as the data may not reach to current date

# We will need these stored
modelnames <- c("SNAIVE", "5-MA", "7-MA", "9-MA", "12-MA", "STL", "ETS", "TBATS", "STLF", "ARIMAX", "DYNREG", "NN", "COMBINED")
```

```{r datasets_weekly, include = FALSE}
# Weekly aggregation is a bit more tricky operation as weekly aggregate gives incorrect results, so we'll use
# a function of our own

red.weekly <- aggregate_weekly(all.red)
Ominus.weekly <- aggregate_weekly(Ominus.distr)
Oplus.weekly <- aggregate_weekly(Oplus.distr)
Aminus.weekly <- aggregate_weekly(Aminus.distr)
Aplus.weekly <- aggregate_weekly(Aplus.distr)
Bminus.weekly <- aggregate_weekly(Bminus.distr)
Bplus.weekly <- aggregate_weekly(Bplus.distr)
ABminus.weekly <- aggregate_weekly(ABminus.distr)
ABplus.weekly <- aggregate_weekly(ABplus.distr)
plat.weekly <- aggregate_weekly(all.plat)

# Create a master frame
weekly <- data.frame(week = red.weekly$week,
                     date = red.weekly$date,
                     red = red.weekly$pcs,
                     Ominus = Ominus.weekly$pcs,
                     Oplus = Oplus.weekly$pcs,
                     Aminus = Aminus.weekly$pcs,
                     Aplus = Aplus.weekly$pcs,
                     Bminus = Bminus.weekly$pcs,
                     Bplus = Bplus.weekly$pcs,
                     ABminus = ABminus.weekly$pcs,
                     ABplus = ABplus.weekly$pcs,
                     plat = plat.weekly$pcs)

wbeginning <- tail(weekly$date, ((rw_years + 1) * 52 + 1))[1] # Define beginning of (weekly) time here
```


ts() accepts two kinds of "start indicators"
```{r}
ts1 <- ts(c(1,2,3,4,5,6,7,8,9,10), start = decimal_date(as.Date("2009-08-01")), frequency=12) # decimal_date
ts1
```
```{r}
ts2 <- ts(c(1,2,3,4,5,6,7,8,9,10), start = c(2009, 8, 1), frequency=12) # integer vector
ts2
```

The bizdays(x, FinCenter=) function wants a time series as x. However, it gets very confused when we used a ts that has been initialized with decimal_date()
```{r}
bizdays(ts1, FinCenter = "Zurich")
```

```{r}
bizdays(ts2, FinCenter = "Zurich")
```
The "bug" went initially unnoticed because decimal_date() outputs a whole integer at the 1st of January (date I likely used for testing this)
```{r}
ts3 <- ts(c(1,2,3,4,5,6,7,8,9,10), start = decimal_date(as.Date("2010-01-01")), frequency=12) # decimal_date
ts3
```

The difference in performance is significant:
```{r}
type <-"red"
html <- draw_history(paste0(MONTHLYDIR, type, "_rwy", rw_years, "_second", ".csv"), monthly_real, freq = "monthly", type, palette)
save_html(html, paste0(MONTHLYDIR, type, ".html"), background = "white", libdir = "lib")
```

```{r}
type <-"red"
html <- draw_history(paste0(MONTHLYDIR, type, "_rwy", rw_years, ".csv"), monthly_real, freq = "monthly", type, palette)
save_html(html, paste0(MONTHLYDIR, type, ".html"), background = "white", libdir = "lib")
```

