---
title: '[DEPRECATED] Forecasting Lab: Red Cell Figures'
output: github_document
---

# Intro
This notebook follows the genral structure of **DEP_adjusted_first_analyses**, but focuses on *RED CELLS*. In addition, first naive benchmarks are added and first experiments with model saving and filters are conducted. This is also severely deprecated.

```{r setup, message=FALSE}
# Set working directory
knitr::opts_knit$set(root.dir = "/home/esa/production_forecasts") # Working on Ubuntu
# knitr::opts_knit$set(root.dir = "V:/production_forecasts") # Working home

library(forecast)
library(ggplot2)
library(gridExtra)
library(knitr)
```


## Create original dataset that should remain immutable throughout labbing
```{r load_data, message=FALSE}
# Load data
monthly_sales <- read.table("./data/kuukausimyynti.txt", header = T, sep = "\t")

# Separate yyyy/mmm column into months and years
monthly_sales$year <- substr(monthly_sales$kuukausi, 1, 4)
monthly_sales$month <- factor(substr(monthly_sales$kuukausi, 6, 8), levels = c("tam", "hel", "maa", "huh", "tou", "kes", "hei", "elo", "syy", "lok", "mar", "jou"))

# Create a numeric column for months
monthly_sales$month_num <- as.numeric(monthly_sales$month)

# Omit empty values
d <- na.omit(monthly_sales)
```

## Create the time series object
```{r create_ts}
ts.red <- ts(d$Punasoluvalmisteet, 
             start = as.numeric(c(d$year[1], d$month_num[1])), 
             end = as.numeric(c(tail(d$year, 1), tail(d$month_num, 1))), 
             frequency = 12)  
autoplot(ts.red) + ggtitle("Monthly sales of red cell products") + ylab("Red cell units")
```

## Naive forecast as a benchmark
```{r naive_benchmark}
naive_plot <- ggplot() 
naive_forecast_errors <- c()
naive_RMSE <- c()
naive_MAPE <- c()
# Loop 
for(i in seq(from = 48, to = 180, by = 1)){
  fit <- naive(head(ts.red, i))  # Fit based on history so far
  fcast <- forecast(fit, h = 1)  # Forecast the next month
  segment <- ts.red[i + 1]  # Extract that year from the history for error calculations
  
  # Build the plot piece by piece
  naive_plot <- naive_plot + autolayer(fcast)
  
  # Calculate raw forecast errors
  naive_forecast_errors <- c(naive_forecast_errors, abs(data.frame(fcast)$Point.Forecast - segment))
  
  naive_RMSE <- c(naive_RMSE, data.frame(accuracy(fcast, segment))$RMSE)
  naive_MAPE <- c(naive_MAPE, data.frame(accuracy(fcast, segment))$MAPE)
}
```

```{r plot_naive}
# Plot
naive_plot + ggtitle("Naive forecast of red cell sales month by month") +
  scale_x_discrete(limits = c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018)) + xlab("Time") +
  ylab("Unit sales") + autolayer(window(ts.red, start = 2008), colour = FALSE) +
  geom_text(aes(2018, 26000, label = paste("RMSE: ", as.name(mean(naive_RMSE))))) + geom_text(aes(2018, 26700, label = paste("MAPE: ", as.name(mean(naive_MAPE)))))
```

## First improvement: Business day adjustment
```{r biz_adj}
# Business day adjustment
ts.red <- ts.red/bizdays(ts.red, FinCenter = "Zurich")  # Zurich is closest to Finnish business calendar, implementing of which would be a chore
```

Redo naive
```{r redo_naive}
naive_adj_plot <- ggplot() 
naive_adj_forecast_errors <- c()
naive_adj_RMSE <- c()
naive_adj_MAPE <- c()
# Loop 
for(i in seq(from = 48, to = 180, by = 1)){
  fit <- naive(head(ts.red, i))  # Fit based on history so far
  fcast <- forecast(fit, h = 1)  # Forecast the next month
  segment <- ts.red[i + 1]  # Extract that year from the history for error calculations
  
  # Build the plot piece by piece
  naive_adj_plot <- naive_adj_plot + autolayer(fcast)
  
  # Calculate raw forecast errors
  naive_adj_forecast_errors <- c(naive_adj_forecast_errors, abs(data.frame(fcast)$Point.Forecast - segment))
  
  naive_adj_RMSE <- c(naive_adj_RMSE, data.frame(accuracy(fcast, segment))$RMSE)
  naive_adj_MAPE <- c(naive_adj_MAPE, data.frame(accuracy(fcast, segment))$MAPE)
}
```

```{r redo_naive_plot}
# Plot
naive_adj_plot + ggtitle("Naive forecast of adjusted red cell sales month by month") +
  scale_x_discrete(limits=c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018)) + xlab("Time") +
  ylab("Unit sales per day") + autolayer(window(ts.red, start = 2008), colour = FALSE) +
  geom_text(aes(2018, 1300, label = paste("RMSE: ", as.name(mean(naive_adj_RMSE))))) + geom_text(aes(2018, 1370, label = paste("MAPE: ", as.name(mean(naive_adj_MAPE)))))
```

Adjusting for business days per month improved the naive forecast by a whopping 1.59 percentage points.

```{r seasonplot}
ggseasonplot(ts.red, year.labels = TRUE, year.labels.left = TRUE) + ggtitle("Red cell yearly seasonality")
```

Seems to me that July is a low point in sales very consistently, while lots of sales happen in April, May and September.

## Old forecasts with better decomp

Old forecasts are built using **STL+ETS** and **ETS** models, including also a naive 6 month repetition forecast. I will not be considering the naive "forecast" here, as I'm fairly certain we want to do proper modelling. Here we will run models on business day adjusted data, which should improve their performance somewhat.
```{r}
# Seasonal and Trend decomposition by LOESS + ETS
# The t.window of stl() should be an odd number, but someone has decided against it here. Will investigate.

# IF MODEL EXISTS ALREADY, LOAD
if (file.exists("./data/models/biz_jarno_stl_red.rds")) {
  stl.red <- readRDS("./data/models/biz_jarno_stl_red.rds")
} else {  # IF IT DOESN'T, CREATE AND SAVE
  stl.red <- forecast(stl(ts.red, s.window = "periodic", t.window = 6), h = 12)
  saveRDS(stl.red, "./data/models/biz_jarno_stl_red.rds")
}



# Exponential smoothing state space model
# ets() is an automated model selection function, so these are not the same model! Uses AICc, AIC and BIC.
if (file.exists("./data/models/biz_jarno_ets_red.rds")) {
  ets.red <- readRDS("./data/models/biz_jarno_ets_red.rds")
} else {
  ets.red <- forecast(ets(ts.red), h = 12)
  saveRDS(ets.red, "./data/models/biz_jarno_ets_red.rds")
}


# Plot
grid.arrange(grobs=list(autoplot(stl.red),
                        autoplot(ets.red)),
             layout_matrix=rbind(c(1),
                                 c(2)))
```

Let's see how the STL performs on business day adjusted data

```{r stl_decomp}
decomposed <- stl(ts.red, s.window = "periodic")  # Seasonal and Trend decomposition using LOESS
seasonal <- decomposed$time.series[, 1]          # Season component
trend <- decomposed$time.series[, 2]             # Trend component
remainder <- decomposed$time.series[, 3]         # Remainder component

autoplot(decomposed)  # Plot
```

The seasonal component looks consistent, but seems to still be smaller than random noise. Let's check the autocorrelation of the remainder to see how well the decomposition works.

```{r stl_remainder_autocorr}
ggAcf(remainder) + ggtitle("Autocorrelation of remainder from stl decomp of adjusted red cell series")
```

There are significant lags at 2 and 7 lags, but otherwise the ACF looks *much* cleaner than before. The business day adjustment seems to be effective. Let's see what kind of forecasts these give.

```{r stl}
stl_adj_plot <- ggplot() 
stl_adj_forecast_errors <- c()
stl_adj_RMSE <- c()
stl_adj_MAPE <- c()
# Loop 
for(i in seq(from = 48, to = 180, by = 1)){
  fit <- stl(head(ts.red, i), s.window = "periodic", t.window = 6)  # Fit based on history so far
  fcast <- forecast(fit, h = 1)  # Forecast the next month
  segment <- ts.red[i + 1]  # Extract that year from the history for plotting purposes
  
  # Build the plot piece by piece
  stl_adj_plot <- stl_adj_plot + autolayer(fcast) # + autolayer(segment, colour=FALSE)
  
  # Calculate raw forecast errors
  stl_adj_forecast_errors <- c(stl_adj_forecast_errors, abs(data.frame(fcast)$Point.Forecast - segment))
  
  stl_adj_RMSE <- c(stl_adj_RMSE, data.frame(accuracy(fcast, segment))$RMSE)
  stl_adj_MAPE <- c(stl_adj_MAPE, data.frame(accuracy(fcast, segment))$MAPE)
}

stl_adj_plot + ggtitle("STL+ETS forecast of adjusted red cell sales month by month") +
  scale_x_discrete(limits = c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018)) + xlab("Time") +
  ylab("Unit sales") + autolayer(window(ts.red, start = 2008), colour = FALSE) +
  geom_text(aes(2018, 1300, label = paste("RMSE: ", as.name(mean(stl_adj_RMSE))))) + geom_text(aes(2018, 1370, label = paste("MAPE: ", as.name(mean(stl_adj_MAPE)))))
```
The naive errors are halved.

```{r ets}
ets_adj_plot <- ggplot() 
ets_adj_forecast_errors <- c()
ets_adj_RMSE <- c()
ets_adj_MAPE <- c()
# Loop 
for(i in seq(from = 48, to = 180, by = 1)){
  fit <- ets(head(ts.red, i))  # Fit based on history so far
  fcast <- forecast(fit, h = 1)  # Forecast the next month
  segment <- ts.red[i + 1]  # Extract that month from the history for error calculation
  
  # Build the plot piece by piece
  ets_adj_plot <- ets_adj_plot + autolayer(fcast)
  
  # Calculate forecast errors
  ets_adj_forecast_errors <- c(ets_adj_forecast_errors, abs(data.frame(fcast)$Point.Forecast - segment))
  
  ets_adj_RMSE <- c(ets_adj_RMSE, data.frame(accuracy(fcast, segment))$RMSE)
  ets_adj_MAPE <- c(ets_adj_MAPE, data.frame(accuracy(fcast, segment))$MAPE)
}

ets_adj_plot + ggtitle("ETS forecast of adjusted red cell sales month by month") +
  scale_x_discrete(limits = c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018)) + xlab("Time") +
  ylab("Unit sales") + autolayer(window(ts.red, start = 2008), colour = FALSE) +
  geom_text(aes(2018, 1300, label = paste("RMSE: ", as.name(mean(ets_adj_RMSE))))) + geom_text(aes(2018, 1370, label = paste("MAPE: ", as.name(mean(ets_adj_MAPE)))))
```


## Trying out more advanced methods of decomposing

```{r multi_decomp}
multi_decomp <- mstl(ts.red)
multi_trend <- multi_decomp[, 2]
multi_season <- multi_decomp[, 3]
multi_remainder <- multi_decomp[, 4]
autoplot(multi_decomp) + ggtitle("Multiple seasonality decomposition")
```


```{r multi_decomp_plot}
# Plot with simple seasonal decomposition to see if there are tangible differences
grid.arrange(grobs = list(autoplot(seasonal) + ggtitle("STL"),
                          autoplot(multi_season) + ggtitle("MSTL")),
             layout_matrix = rbind(c(1),
                                   c(2)))
```

The MSTL has a slight decrease in the magnitude of the seasonality.

```{r autocorr_comparison}
# Let's compare their autocorrelation plots
grid.arrange(grobs = list(ggAcf(remainder) + ggtitle("STL remainder"),
                          ggAcf(multi_remainder) + ggtitle("MSTL remainder")),
             layout_matrix = rbind(c(1),
                                   c(2)))
```

Somewhat surprisingly it seems that the simpler STL decomposition is more accurate. Let's confirm by CV.

```{r cv_comparison_multi_vs_simple}
stl_multi_plot <- ggplot() 
stl_multi_forecast_errors <- c()
stl_multi_RMSE <- c()
stl_multi_MAPE <- c()
# Loop 
for(i in seq(from = 48, to = 180, by = 1)){
  fit <- stlf(head(ts.red, i), s.window = "periodic", t.window = 6)  # Fit based on history so far
  fcast <- forecast(fit, h = 1)  # Forecast the next month
  segment <- ts.red[i + 1]  # Extract that year from the history for plotting purposes
  
  # Build the plot piece by piece
  stl_multi_plot <- stl_multi_plot + autolayer(fcast) # + autolayer(segment, colour=FALSE)
  
  # Calculate raw forecast errors
  stl_multi_forecast_errors <- c(stl_multi_forecast_errors, abs(data.frame(fcast)$Point.Forecast - segment))
  
  stl_multi_RMSE <- c(stl_multi_RMSE, data.frame(accuracy(fcast, segment))$RMSE)
  stl_multi_MAPE <- c(stl_multi_MAPE, data.frame(accuracy(fcast, segment))$MAPE)
}

stl_multi_plot + ggtitle("STLF forecast of adjusted red cell sales month by month") +
  scale_x_discrete(limits = c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018)) + xlab("Time") +
  ylab("Unit sales") + autolayer(window(ts.red, start = 2008), colour = FALSE) +
  geom_text(aes(2018, 1300, label = paste("RMSE: ", as.name(mean(stl_multi_RMSE))))) + geom_text(aes(2018, 1370, label = paste("MAPE: ", as.name(mean(stl_multi_MAPE)))))
```

The results are exactly the same to the 5th decimal point! It appears that Multiple Seasonal Decomposition has no advantage over simple STL.

Let's do this again, but with filtering and see if it could improve the results
```{r filtering_1}
# Filter
smooth25.red <- ts(itsmr::smooth.fft(ts.red, .25), start = as.numeric(c(d$year[1], d$month_num[1])), 
                   end = as.numeric(c(tail(d$year, 1), tail(d$month_num, 1))), frequency = 12)
smooth10.red <- ts(itsmr::smooth.fft(ts.red, .1), start = as.numeric(c(d$year[1], d$month_num[1])),
                   end = as.numeric(c(tail(d$year, 1), tail(d$month_num, 1))), frequency = 12)

cnct.smooth25 <- ts(itsmr::smooth.fft(head(ts.red, 24), .25), start = as.numeric(c(d$year[1], d$month_num[1])), frequency = 12)
autoplot(smooth25.red, colour = "red") + autolayer(smooth10.red, colour = FALSE) + ggtitle(".10 and .25 smoothed ts.red") + autolayer(cnct.smooth25, colour = TRUE)
```

The filtering changes as we move down the time stream. We'll try to incorporate this into the CV.

We'll need to cut off the end of the series as the smoothing produces an awkwardly aggressive slope at the end. Or do we? Will investigate.
```{r filtering_concat}
smooth25.red <- head(smooth25.red, 180)
smooth10.red <- head(smooth10.red, 180)
autoplot(smooth25.red, colour = "red") + autolayer(smooth10.red, colour = FALSE)

```


## Old forecasts now with filtering
```{r filtered_forecast}
# Seasonal and Trend decomposition by LOESS + ETS
# The t.window of stl() should be an odd number, but someone has decided against it here. Will investigate.

# IF MODEL EXISTS ALREADY, LOAD
if (file.exists("./data/models/biz_smooth25_jarno_stl_red.rds")) {
  smooth25.stl.red <- readRDS("./data/models/biz_smooth25_jarno_stl_red.rds")
} else {  # IF IT DOESN'T, CREATE AND SAVE
  smooth25.stl.red <- forecast(stl(smooth25.red, s.window="periodic", t.window = 6), h = 12)
  saveRDS(smooth25.stl.red, "./data/models/biz_smooth25_jarno_stl_red.rds")
}

if (file.exists("./data/models/biz_smooth10_jarno_stl_red.rds")) {
  smooth10.stl.red <- readRDS("./data/models/biz_smooth10_jarno_stl_red.rds")
} else {  # IF IT DOESN'T, CREATE AND SAVE
  smooth10.stl.red <- forecast(stl(smooth10.red, s.window="periodic", t.window = 6), h = 12)
  saveRDS(smooth10.stl.red, "./data/models/biz_smooth10_jarno_stl_red.rds")
}

# Exponential smoothing state space model
# ets() is an automated model selection function, so these are not the same model! Uses AICc, AIC and BIC.
if (file.exists("./data/models/biz_smooth25_jarno_ets_red.rds")) {
  smooth25.ets.red <- readRDS("./data/models/biz_smooth25_jarno_ets_red.rds")
} else {
  smooth25.ets.red <- forecast(ets(smooth25.red), h = 12)
  saveRDS(smooth25.ets.red, "./data/models/biz_smooth25_jarno_ets_red.rds")
}

if (file.exists("./data/models/biz_smooth10_jarno_ets_red.rds")) {
  smooth10.ets.red <- readRDS("./data/models/biz_smooth10_jarno_ets_red.rds")
} else {
  smooth10.ets.red <- forecast(ets(smooth10.red), h = 12)
  saveRDS(smooth10.ets.red, "./data/models/biz_smooth10_jarno_ets_red.rds")
}

# Plot
grid.arrange(grobs = list(autoplot(smooth25.stl.red),
                          autoplot(smooth25.ets.red),
                          autoplot(smooth10.stl.red),
                          autoplot(smooth10.ets.red)),
             layout_matrix = rbind(c(1, 2),
                                   c(3, 4)))
```
These give somewhat nonsensical forecasts. The smoothing isn't robust for "pathological" observations at the end I suppose? 

Let's see how these perform in CV
```{r filtered25_errors}
stl_smooth_plot <- ggplot() 
stl_smooth_forecast_errors <- c()
stl_smooth_RMSE <- c()
stl_smooth_MAPE <- c()
# Loop 
for(i in seq(from = 48, to = 180, by = 1)){
  fit <- stl(head(smooth25.red, i), s.window = "periodic", t.window = 6)  # Fit based on history so far
  fcast <- forecast(fit, h = 1)  # Forecast the next month
  segment <- ts.red[i + 1]  # Extract that year from the history for errror
  
  # Build the plot piece by piece
  stl_smooth_plot <- stl_smooth_plot + autolayer(fcast) # + autolayer(segment, colour=FALSE)
  
  # Calculate raw forecast errors
  stl_smooth_forecast_errors <- c(stl_smooth_forecast_errors, abs(data.frame(fcast)$Point.Forecast - segment))
  
  stl_smooth_RMSE <- c(stl_smooth_RMSE, data.frame(accuracy(fcast, segment))$RMSE)
  stl_smooth_MAPE <- c(stl_smooth_MAPE, data.frame(accuracy(fcast, segment))$MAPE)
}

stl_smooth_plot + ggtitle("STL forecast of adjusted smoothed (.25) red cell sales month by month") +
  scale_x_discrete(limits=c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018)) + xlab("Time") +
  ylab("Unit sales") + autolayer(window(ts.red, start = 2008), colour = FALSE) +
  geom_text(aes(2018, 1300, label = paste("RMSE: ", as.name(mean(stl_smooth_RMSE))))) + geom_text(aes(2018, 1370, label = paste("MAPE: ", as.name(mean(stl_smooth_MAPE)))))
```

```{r filtered10_errors}
stl_smooth10_plot <- ggplot() 
stl_smooth10_forecast_errors <- c()
stl_smooth10_RMSE <- c()
stl_smooth10_MAPE <- c()
# Loop 
for(i in seq(from = 48, to = 180, by = 1)){
  fit <- stl(head(smooth10.red, i), s.window = "periodic", t.window = 6)  # Fit based on history so far
  fcast <- forecast(fit, h = 1)  # Forecast the next month
  segment <- ts.red[i + 1]  # Extract that year from the history for errror
  
  # Build the plot piece by piece
  stl_smooth10_plot <- stl_smooth10_plot + autolayer(fcast) # + autolayer(segment, colour=FALSE)
  
  # Calculate raw forecast errors
  stl_smooth10_forecast_errors <- c(stl_smooth10_forecast_errors, abs(data.frame(fcast)$Point.Forecast - segment))
  
  stl_smooth10_RMSE <- c(stl_smooth10_RMSE, data.frame(accuracy(fcast, segment))$RMSE)
  stl_smooth10_MAPE <- c(stl_smooth10_MAPE, data.frame(accuracy(fcast, segment))$MAPE)
}

stl_smooth10_plot + ggtitle("STL forecast of adjusted smoothed (.10) red cell sales month by month") +
  scale_x_discrete(limits = c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018)) + xlab("Time") +
  ylab("Unit sales") + autolayer(window(ts.red, start = 2008), colour = FALSE) +
  geom_text(aes(2018, 1300, label = paste("RMSE: ", as.name(mean(stl_smooth10_RMSE))))) + geom_text(aes(2018, 1370, label = paste("MAPE: ", as.name(mean(stl_smooth10_MAPE)))))
```

## Model comparisons
```{r regular_stl}
monthly <- ggplot() 
forecast_errors <- c()
stl_RMSE <- c()
stl_MAPE <- c()
# Loop 
for(i in seq(from = 48, to = 180, by = 1)){
  fit <- stl(head(ts.red, i), s.window = "periodic", t.window = 6)  # Fit based on history so far
  fcast <- forecast(fit, h = 1)  # Forecast the next month
  segment <- ts.red[i + 1]  # Extract that year from the history for plotting purposes
  
  # Build the plot piece by piece
  monthly <- monthly + autolayer(fcast) # + autolayer(segment, colour=FALSE)
  
  # Calculate raw forecast errors
  forecast_errors <- c(forecast_errors, abs(data.frame(fcast)$Point.Forecast - segment))
  
  stl_RMSE <- c(stl_RMSE, data.frame(accuracy(fcast, segment))$RMSE)
  stl_MAPE <- c(stl_MAPE, data.frame(accuracy(fcast, segment))$MAPE)
}

monthly + ggtitle("STL+ETS forecast of red cell sales month by month") +
  scale_x_discrete(limits = c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018)) + xlab("Time") +
  ylab("Unit sales") + autolayer(window(ts.red, start = 2008), colour = FALSE)  +
  geom_text(aes(2018, 1300, label = paste("RMSE: ", as.name(mean(stl_RMSE))))) + geom_text(aes(2018, 1370, label = paste("MAPE: ", as.name(mean(stl_MAPE)))))
```


```{r stl_historical_errors}
autoplot(ts(forecast_errors, start = 2008, end = 2018, frequency = 12)) + ggtitle("STL+ETS historical forecast errors for red cells") + ylab("Unit sales")
```


```{r regular_ets}
monthly_ets <- ggplot() 
ets_forecast_errors <- c()
ets_RMSE <- c()
ets_MAPE <- c()
# Loop 
for(i in seq(from = 48, to = 180, by = 1)){
  fit <- ets(head(ts.red, i))  # Fit based on history so far
  fcast <- forecast(fit, h = 1)  # Forecast the next month
  segment <- ts.red[i + 1]  # Extract that month from the history for error calculation
  
  # Build the plot piece by piece
  monthly_ets <- monthly_ets + autolayer(fcast)
  
  # Calculate forecast errors
  ets_forecast_errors <- c(ets_forecast_errors, abs(data.frame(fcast)$Point.Forecast - segment))
  
  ets_RMSE <- c(ets_RMSE, data.frame(accuracy(fcast, segment))$RMSE)
  ets_MAPE <- c(ets_MAPE, data.frame(accuracy(fcast, segment))$MAPE)
}

monthly_ets + ggtitle("ETS forecast of red cell sales year by year") +
  scale_x_discrete(limits = c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018)) + xlab("Time") +
  ylab("Unit sales") + autolayer(window(ts.red, start = 2008), colour=FALSE)  +
  geom_text(aes(2018, 1300, label = paste("RMSE: ", as.name(mean(ets_RMSE))))) + geom_text(aes(2018, 1370, label = paste("MAPE: ", as.name(mean(ets_MAPE)))))
```


```{r ets_historical_errors}
autoplot(ts(ets_forecast_errors, start = 2008, end = 2018, frequency = 12)) + ggtitle("ETS historical forecast errors for red cells") + ylab("Unit sales")
```

## How far back do the models actually look?
```{r stl_5_rolling}
##################################
# 5 YEARS
##################################
monthly_5yr <- ggplot() 
forecast_errors_5yr <- c()
stl_RMSE_5yr <- c()
stl_MAPE_5yr <- c()
# Loop 
for(i in seq(from = 48, to = 180, by = 1)){
  fit <- stl(tail(head(ts.red, i), 60), s.window = "periodic", t.window = 6)  # Fit based on 5yr history
  fcast <- forecast(fit, h = 1)  # Forecast the next month
  segment <- ts.red[i + 1]  # Extract that month from the history for error calculation
  
  # Build the plot piece by piece
  monthly_5yr <- monthly_5yr + autolayer(fcast)
  
  # Calculate raw forecast errors
  forecast_errors_5yr <- c(forecast_errors_5yr, abs(data.frame(fcast)$Point.Forecast - segment))
  
  stl_RMSE_5yr <- c(stl_RMSE_5yr, data.frame(accuracy(fcast, segment))$RMSE)
  stl_MAPE_5yr <- c(stl_MAPE_5yr, data.frame(accuracy(fcast, segment))$MAPE)
}

monthly_5yr + ggtitle("STL+ETS forecast of red cell sales month by month, 5 years of data") +
  scale_x_discrete(limits = c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018)) + xlab("Time") +
  ylab("Unit sales") + autolayer(window(ts.red, start = 2008), colour = FALSE) +
  geom_text(aes(2018, 1300, label = paste("RMSE: ", as.name(mean(stl_RMSE_5yr))))) + geom_text(aes(2018, 1370, label = paste("MAPE: ", as.name(mean(stl_MAPE_5yr)))))
```


```{r stl_3_rolling}
##################################
# 3 YEARS
##################################
monthly_3yr <- ggplot() 
forecast_errors_3yr <- c()
stl_RMSE_3yr <- c()
stl_MAPE_3yr <- c()
# Loop 
for(i in seq(from = 48, to = 180, by = 1)){
  fit <- stl(tail(head(ts.red, i), 36), s.window = "periodic", t.window = 6)  # Fit based on 3yr history
  fcast <- forecast(fit, h = 1)  # Forecast the next month
  segment <- ts.red[i + 1]  # Extract that month from the history for error calculation
  
  # Build the plot piece by piece
  monthly_3yr <- monthly_3yr + autolayer(fcast)
  
  # Calculate raw forecast errors
  forecast_errors_3yr <- c(forecast_errors_3yr, abs(data.frame(fcast)$Point.Forecast - segment))
  
  stl_RMSE_3yr <- c(stl_RMSE_3yr, data.frame(accuracy(fcast, segment))$RMSE)
  stl_MAPE_3yr <- c(stl_MAPE_3yr, data.frame(accuracy(fcast, segment))$MAPE)
}

monthly_3yr + ggtitle("STL+ETS forecast of red cell sales month by month, 3 years of data") +
  scale_x_discrete(limits = c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018)) + xlab("Time") +
  ylab("Unit sales") + autolayer(window(ts.red, start = 2008), colour = FALSE)  +
  geom_text(aes(2018, 1300, label = paste("RMSE: ", as.name(mean(stl_RMSE_3yr))))) + geom_text(aes(2018, 1370, label = paste("MAPE: ", as.name(mean(stl_MAPE_3yr)))))
```

```{r ets_5_rolling}
##################################
# 5 YEARS
##################################

monthly_ets_5yr <- ggplot() 
ets_forecast_errors_5yr <- c()
ets_RMSE_5yr <- c()
ets_MAPE_5yr <- c()
# Loop 
for(i in seq(from = 48, to = 180, by = 1)){
  fit <- ets(tail(head(ts.red, i), 60))  # Fit based on 5yr history
  fcast <- forecast(fit, h = 1)  # Forecast the next month
  segment <- ts.red[i + 1]  # Extract that month from the history for error calculation
  
  # Build the plot piece by piece
  monthly_ets_5yr <- monthly_ets_5yr + autolayer(fcast)
  
  # Calculate forecast errors
  ets_forecast_errors_5yr <- c(ets_forecast_errors_5yr, abs(data.frame(fcast)$Point.Forecast - segment))
  
  ets_RMSE_5yr <- c(ets_RMSE_5yr, data.frame(accuracy(fcast, segment))$RMSE)
  ets_MAPE_5yr <- c(ets_MAPE_5yr, data.frame(accuracy(fcast, segment))$MAPE)
}

monthly_ets_5yr + ggtitle("ETS forecast of red cell sales month by month, 5 years of data") +
  scale_x_discrete(limits = c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018)) + xlab("Time") +
  ylab("Unit sales") + autolayer(window(ts.red, start = 2008), colour = FALSE)  +
  geom_text(aes(2018, 1300, label = paste("RMSE: ", as.name(mean(ets_RMSE_5yr))))) + geom_text(aes(2018, 1370, label = paste("MAPE: ", as.name(mean(ets_MAPE_5yr)))))
```


```{r ets_3_rolling}
##################################
# 3 YEARS
##################################

monthly_ets_3yr <- ggplot() 
ets_forecast_errors_3yr <- c()
ets_RMSE_3yr <- c()
ets_MAPE_3yr <- c()
# Loop 
for(i in seq(from = 48, to = 180, by = 1)){
  fit <- ets(tail(head(ts.red, i), 36))  # Fit based on 3yr history
  fcast <- forecast(fit, h = 1)  # Forecast the next month
  segment <- ts.red[i + 1]  # Extract that month from the history for error calculation
  
  # Build the plot piece by piece
  monthly_ets_3yr <- monthly_ets_3yr + autolayer(fcast)
  
  # Calculate forecast errors
  ets_forecast_errors_3yr <- c(ets_forecast_errors_3yr, abs(data.frame(fcast)$Point.Forecast - segment))
  
  ets_RMSE_3yr <- c(ets_RMSE_3yr, data.frame(accuracy(fcast, segment))$RMSE)
  ets_MAPE_3yr <- c(ets_MAPE_3yr, data.frame(accuracy(fcast, segment))$MAPE)
}

monthly_ets_3yr + ggtitle("ETS forecast of red cell sales month by month, 3 years of data") +
  scale_x_discrete(limits = c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018)) + xlab("Time") +
  ylab("Unit sales") + autolayer(window(ts.red, start = 2008), colour = FALSE)  +
  geom_text(aes(2018, 1300, label = paste("RMSE: ", as.name(mean(ets_RMSE_3yr))))) + geom_text(aes(2018, 1370, label = paste("MAPE: ", as.name(mean(ets_MAPE_3yr)))))
```

## Forecasting from 2012 onwards
```{r stl_2012}
monthly_2012 <- ggplot() 
forecast_errors_2012 <- c()
stl_RMSE_2012 <- c()
stl_MAPE_2012 <- c()
# Loop 
for(i in seq(from = 96, to = 180, by = 1)){
  fit <- stl(head(ts.red, i), s.window = "periodic", t.window = 6)  # Fit based on history from 2012
  fcast <- forecast(fit, h = 1)  # Forecast the next month
  segment <- ts.red[i + 1]  # Extract that year from the history for plotting purposes
  
  # Build the plot piece by piece
  monthly_2012 <- monthly_2012 + autolayer(fcast) # + autolayer(segment, colour=FALSE)
  
  # Calculate raw forecast errors
  forecast_errors_2012 <- c(forecast_errors_2012, abs(data.frame(fcast)$Point.Forecast - segment))
  
  stl_RMSE_2012 <- c(stl_RMSE_2012, data.frame(accuracy(fcast, segment))$RMSE)
  stl_MAPE_2012 <- c(stl_MAPE_2012, data.frame(accuracy(fcast, segment))$MAPE)
}

monthly_2012 + ggtitle("STL+ETS forecast of red cell sales month by month from 2012") +
  scale_x_discrete(limits = c(2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018)) + xlab("Time") +
  ylab("Unit sales") + autolayer(window(ts.red, start = 2011), colour = FALSE)  +
  geom_text(aes(2018, 1300, label = paste("RMSE: ", as.name(mean(stl_RMSE_2012))))) + geom_text(aes(2018, 1370, label = paste("MAPE: ", as.name(mean(stl_MAPE_2012)))))
```

## Playing around with a NN
```{r N}
monthly_NN <- ggplot() 
NN_forecast_errors <- c()
NN_RMSE <- c()
NN_MAPE <- c()
# Loop 
for(i in seq(from = 48, to = 180, by = 1)){
  fit <- nnetar(head(ts.red, i), lambda = 0)  # Fit based on history
  fcast <- forecast(fit, PI = TRUE, h = 1)  # Forecast the next month
  segment <- ts.red[i + 1]  # Extract that month from the history for error calculation
  
  # Build the plot piece by piece
  monthly_NN <- monthly_NN + autolayer(fcast)
  
  # Calculate forecast errors
  NN_forecast_errors <- c(NN_forecast_errors, abs(data.frame(fcast)$Point.Forecast - segment))
  
  NN_RMSE <- c(NN_RMSE, data.frame(accuracy(fcast, segment))$RMSE)
  NN_MAPE <- c(NN_MAPE, data.frame(accuracy(fcast, segment))$MAPE)
}

monthly_NN + ggtitle("NN forecast of red cell sales month by month") +
  scale_x_discrete(limits = c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018)) + xlab("Time") +
  ylab("Unit sales") + autolayer(window(ts.red, start = 2008), colour = FALSE)  +
  geom_text(aes(2018, 1300, label = paste("RMSE: ", as.name(mean(NN_RMSE))))) + geom_text(aes(2018, 1370, label = paste("MAPE: ", as.name(mean(NN_MAPE)))))
#fit <- nnetar(ts.red, lambda=0)
#autoplot(forecast(fit, PI=TRUE, h=12))
```

Find out which performed better on average:
```{r table_results}
results <- matrix(c(mean(stl_RMSE), mean(stl_MAPE), 
                    mean(ets_RMSE), mean(ets_MAPE),
                    mean(NN_RMSE), mean(NN_MAPE),
                    mean(stl_multi_RMSE), mean(stl_multi_MAPE),
                    mean(stl_RMSE_3yr), mean(stl_MAPE_3yr),
                    mean(ets_RMSE_3yr), mean(ets_MAPE_3yr),
                    mean(stl_RMSE_5yr), mean(stl_MAPE_5yr),
                    mean(ets_RMSE_5yr), mean(ets_MAPE_5yr),
                    mean(stl_RMSE_2012), mean(stl_MAPE_2012)), 
                  ncol = 2, 
                  byrow = TRUE)

colnames(results) <- c("RMSE", "MAPE")
rownames(results) <- c("STL+ETS whole", 
                       "ETS whole",
                       "NN whole",
                       "STLF whole",
                       "STL+ETS 3yr",
                       "ETS 3yr",
                       "STL+ETS 5yr",
                       "ETS 5yr",
                       "STL+ETS 2012")

results <- kable(results, "markdown")
results
```
