---
title: "Production Forecasts"
output: html_document
---

```{r setup, echo = FALSE}
# Set working directory
knitr::opts_chunk$set(root.dir = "/home/esa/production_forecasts", warning = FALSE, message = FALSE) # No warnings for final output
knitr::opts_knit$set(root.dir = "/home/esa/production_forecasts") # Working on Ubuntu

# Colorblind palette
# black, orange, sky blue, green,
# yellow, blue, vermilion, purple
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
                "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# These colors work server side for now:
palette <- list(1, 1, 1, 0.7, "royalblue2", "deepskyblue1", "darkred", "darkgreen")
names(palette) <- c("alpha80", "alpha95", "alphaSeg", "alphaPred", "fill80", "fill95", "colPred", "colData")
```

```{r imports, message = FALSE, echo = FALSE}
library(forecast)
library(ggplot2)
library(gridExtra)
library(knitr)
library(plyr)
library(lubridate)
library(numbers)
library(data.table)
library(R.utils)
library(DT)
source("src/pffunctions.R")
```

```{r read_files, include = FALSE}
# Get all the files
PATH <- "/home/esa/production_forecasts/data/FACS/"
files <- list.files(path = PATH, pattern = "FAC0091_*")  # Character vector of file names

# Compile a dataframe by going over all files
dlist <- list()
for (i in files) {
  # Read a single file to a df called d
  d <- read.delim(file = paste0(PATH, "/", i), header = FALSE, sep = ";", stringsAsFactors = FALSE, colClasses = 'character')
  
  if(length(d) == 26){
    d <- d[, !(names(d) %in% c("V10"))]  # The column numbers unfortunately vary between files, so we'll adjust
    }
  
  colnames(d) <- c("V1", "V2", "V3", "V4", "V5", "V6", "V7", "V8", "V9", "V10",
                   "V11", "V12", "V13", "V14", "V15", "V16", "V17", "V18", "V19", "V20",
                   "V21", "V22", "V23", "V24", "V25")  # This is done so as to have easier column handling later on
  dlist[[i]] <- d
}

d <- as.data.frame(rbindlist(dlist, fill = TRUE))
```

```{r modify_dataframe, include = FALSE}
# Divide into distributions (P) and returns (R)
P <- d[d$V1 == "P", ]
R <- d[d$V1 == "R", ]

# For distributions, we'll keep Distribution date, Quantity, ABO type, Volume, Exp date
keep <- c("V12", "V14", "V18", "V20", "V22", "V24")
distr <- P[keep]
colnames(distr) <- c("date", "product", "quantity", "ABO", "volume", "exp")

# For returns we keep the return date and quantity
keep <- c("V4", "V7")
retrn <- R[keep]
colnames(retrn) <- c("date", "quantity")

# Datify
distr$date <- dmy(distr$date); distr$exp <- dmy(distr$exp)
retrn$date <- dmy(retrn$date)

# Numerify
distr$quantity <- as.numeric(distr$quantity); distr$volume <- as.numeric(distr$volume)
retrn$quantity <- as.numeric(retrn$quantity)

# Product codes for red cell products
red.codes <- c("budTR001", "A0071V00", "A0074V00", "A0092VA0", "A0092VB0", 
               "E3844V00", "E3845V00", "E3846VA0", "E3846VB0", "E3846VC0",
               "E3846V00", "E3847VA0", "E3847VB0", "E3847VC0", "E3847V00",
               "E3936VA0", "E3936VB0", "E3939V00", "E3940V00", "E4683V00",
               "E7668V00", "E7673V00", "E4999V00", "E5000V00")

red.distr <- distr[distr$product %in% red.codes, ]

# Product codes for platelets
plat.codes <- c("budTR002", "trEnnApu", "A0004V00", "A0005V00", "A0006V00", "A0007V00", "A0008V00",
                "A0086VA0", "A0086VB0", "A0086V00", "A0088V00", "A0088VA0", "A0088VB0", "A0089V00",
                "A0089VB0", "A0089VA0", "A0090V00", "A0090VA0", "A0090VB0", "A0018V00", "A0020V00", 
                "A0021V00", "A0021VA0", "A0021VB0", "A0047V00", "A0049V00", "A0051V00", "A0054V00",
                "A0055V00", "A0056V00", "A0057V00", "A0059V00", "A0060V00", "A0067VA0", "A0067VB0",
                "A0067V00", "A0068VA0", "A0068VB0", "A0068V00", "A0075V00", "A0101V00", "A0102V00",
                "E3949V00", "E3953V00", "E3954V00", "E3955V00", "E3956V00", "E3957V00", "E3958V00",
                "E3959V00", "E3960V00", "E3961V00", "E3962V00", "E3963V00", "E3964V00", "E3965V00", 
                "E3966V00", "E3968VA0", "E3968VB0", "E3968V00", "E3970V00", "E3971V00", "E3973V00",
                "E3974V00", "E3976V00", "E3981V00", "E3995V00", "E3996V00", "E3997V00", "E3997VA0",
                "E3997VB0", "E4002V00", "E4004V00", "E6782V00", "E6783V00", "E6953V00", "E6860V00",
                "E6874VA0", "E6874V00", "E6874VB0", "E6875VB0", "E6875V00", "E7530V00", "E7530VA0",
                "E7530VB0", "E7531V00", "E7531VA0", "E7531VB0", "E6875VA0")

plat.distr <- distr[distr$product %in% plat.codes, ]
```

```{r create_datasets, include = FALSE}
# Create a full sequence of dates for imputation purposes
all.dates <- (seq.Date(min(red.distr$date),
                       max(red.distr$date),
                       "day"))
###           ###
#   RED CELLS   #
###           ###
all.red <- aggregate(red.distr$quantity, by = list(red.distr$date), sum); colnames(all.red) <- c("date", "pcs")
# Merge into a whole set with NAs
all.red <- merge(x = data.frame(date = all.dates),
                 y = all.red,
                 all.x = TRUE)
# Replace with zeroes
all.red[is.na(all.red)] <- 0
# Cut to time after 2014
all.red <- all.red[all.red$date >= as.Date("2014-01-06"), ]


# Extracting types
Ominus.distr <- extract_type(red.distr, "O -")  # This our custom function, see pffunctions.R
Oplus.distr <- extract_type(red.distr, "O +")
Aminus.distr <- extract_type(red.distr, "A -")
Aplus.distr <- extract_type(red.distr, "A +")
Bminus.distr <- extract_type(red.distr, "B -")
Bplus.distr <- extract_type(red.distr, "B +")
ABminus.distr <- extract_type(red.distr, "AB-")
ABplus.distr <- extract_type(red.distr, "AB+")


###           ###
#   PLATELETS   #
###           ###
all.plat <- aggregate(plat.distr$quantity, by = list(plat.distr$date), sum); colnames(all.plat) <- c("date", "pcs")
# Merge into a whole set with NAs
all.plat <- merge(x = data.frame(date = all.dates),
                  y = all.plat,
                  all.x = TRUE)
# Replace with zeroes
all.plat[is.na(all.plat)] <- 0
# Cut to time after 2014
all.plat <- all.plat[all.plat$date >= as.Date("2014-01-06"), ]
```

```{r datasets_monthly, include = FALSE, warning = FALSE}
# Aggregate all by months
red.monthly <- aggregate(pcs ~ month(date) + year(date), data = all.red, FUN = sum)
Ominus.monthly <- aggregate(pcs ~ month(date) + year(date), data = Ominus.distr, FUN = sum)
Oplus.monthly <- aggregate(pcs ~ month(date) + year(date), data = Oplus.distr, FUN = sum)
Aminus.monthly <- aggregate(pcs ~ month(date) + year(date), data = Aminus.distr, FUN = sum)
Aplus.monthly <- aggregate(pcs ~ month(date) + year(date), data = Aplus.distr, FUN = sum)
Bminus.monthly <- aggregate(pcs ~ month(date) + year(date), data = Bminus.distr, FUN = sum)
Bplus.monthly <- aggregate(pcs ~ month(date) + year(date), data = Bplus.distr, FUN = sum)
ABminus.monthly <- aggregate(pcs ~ month(date) + year(date), data = ABminus.distr, FUN = sum)
ABplus.monthly <- aggregate(pcs ~ month(date) + year(date), data = ABplus.distr, FUN = sum)
plat.monthly <- aggregate(pcs ~ month(date) + year(date), data = all.plat, FUN = sum)

# Dates
months <- seq(from = as.Date("2014-01-06"), to = max(distr$date), by = "month")

# Adjustment series
adj <- as.numeric(bizdays(ts(months, start = decimal_date(as.Date("2014-01-06")), frequency = 12), FinCenter = "Zurich"))
# scaler <- as.numeric(bizdays(ts(1, start = decimal_date(months[length(months)]), frequency = 12), FinCenter = "Zurich")) This was written to scale a singular forecasted month back to real values, for saving-to-file purposes

reverse_adj <- as.numeric(bizdays(ts(seq(23), start = decimal_date(months[length(months)]), frequency = 12), FinCenter = "Zurich")) # This is the old implementation that used to be fed into the forecasting function. We'll now repurpose it so it can be used both for tabling and plotting.

# Create a master frame
monthly <- data.frame(date = months,
                      red = red.monthly$pcs/adj,
                      Ominus = Ominus.monthly$pcs/adj,
                      Oplus = Oplus.monthly$pcs/adj,
                      Aminus = Aminus.monthly$pcs/adj,
                      Aplus = Aplus.monthly$pcs/adj,
                      Bminus = Bminus.monthly$pcs/adj,
                      Bplus = Bplus.monthly$pcs/adj,
                      ABminus = ABminus.monthly$pcs/adj,
                      ABplus = ABplus.monthly$pcs/adj,
                      plat = plat.monthly$pcs/adj)

monthly_real <- data.frame(date = months,
                           red = red.monthly$pcs,
                           Ominus = Ominus.monthly$pcs,
                           Oplus = Oplus.monthly$pcs,
                           Aminus = Aminus.monthly$pcs,
                           Aplus = Aplus.monthly$pcs,
                           Bminus = Bminus.monthly$pcs,
                           Bplus = Bplus.monthly$pcs,
                           ABminus = ABminus.monthly$pcs,
                           ABplus = ABplus.monthly$pcs,
                           plat = plat.monthly$pcs)

beginning <- head(tail(monthly$date, 49), 1) # Define beginning of (monthly) time here
last_month <- tail(monthly_real$date, 1) # Not using "today()" as the data may not reach to current date

# We will need these stored
modelnames <- c("ETS", "STL", "TBATS", "STLF", "LMx2", "NAIVE", "SNAIVE", "RWF", "MEANF",
                "ETS.25", "STL.25", "TBATS.25", "STLF.25", "LMx2.25", "NAIVE.25", "SNAIVE.25", "RWF.25", "MEANF.25",
                "ETS.10", "STL.10", "TBATS.10", "STLF.10", "LMx2.10", "NAIVE.10", "SNAIVE.10", "RWF.10", "MEANF.10")
```

```{r datasets_weekly, include = FALSE}
# Weekly aggregation is a bit more tricky operation as weekly aggregate gives incorrect results, so we'll use
# a function of our own

red.weekly <- aggregate_weekly(all.red)
Ominus.weekly <- aggregate_weekly(Ominus.distr)
Oplus.weekly <- aggregate_weekly(Oplus.distr)
Aminus.weekly <- aggregate_weekly(Aminus.distr)
Aplus.weekly <- aggregate_weekly(Aplus.distr)
Bminus.weekly <- aggregate_weekly(Bminus.distr)
Bplus.weekly <- aggregate_weekly(Bplus.distr)
ABminus.weekly <- aggregate_weekly(ABminus.distr)
ABplus.weekly <- aggregate_weekly(ABplus.distr)
plat.weekly <- aggregate_weekly(all.plat)

# Create a master frame
weekly <- data.frame(week = red.weekly$week,
                     startdate = red.weekly$startdate,
                     red = red.weekly$pcs,
                     Ominus = Ominus.weekly$pcs,
                     Oplus = Oplus.weekly$pcs,
                     Aminus = Aminus.weekly$pcs,
                     Aplus = Aplus.weekly$pcs,
                     Bminus = Bminus.weekly$pcs,
                     Bplus = Bplus.weekly$pcs,
                     ABminus = ABminus.weekly$pcs,
                     ABplus = ABplus.weekly$pcs,
                     plat = plat.weekly$pcs)

wbeginning <- head(tail(weekly$startdate, 209), 1) # Define beginning of (weekly) time here
```

## 6 month forecast {.tabset .tabset-fade .tabset-pills}

### All red
```{r monthly_model_selection_red, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(monthly$red, 49), 48)
series.ts <- ts(segment, start = decimal_date(beginning), frequency = 12)

chosen.model <- select_model(segment, beginning, series.ts, "monthly")
modelname <- modelnames[chosen.model]
```

```{r monthly_fcast_red, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "monthly")

# Extended for yearly estimates
# TODO: Why does this give ever increasing estimates?
fdf_for_tables <- chosen_forecast_extended(chosen.model, series.ts, freq = "monthly")

# Scalings
fdf_for_plots <- fdf * reverse_adj[1:6] # We plot 6 months forward
fdf_red_for_tables <- fdf_for_tables * reverse_adj # The tables need anything from 6 months to 23 months, so we just scale everything from the extended 
```

```{r save_monthly_red, echo = FALSE}
save_forecast(fdf, months = TRUE, modelname, "histories/monthly_red.csv") # Check pffunctions.R
```

```{r, monthly_red_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf_for_plots, freq = "monthly", monthly_real, "red",  modelname, palette) # Check pffunctions.R
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for `r as.character(lubridate::month(today(), label = TRUE, abbr = FALSE))` `r lubridate::year(today())`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### O-
```{r monthly_model_selection_Ominus, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(monthly$Ominus, 49), 48)
series.ts <- ts(segment, start = decimal_date(beginning), frequency = 12)

chosen.model <- select_model(segment, beginning, series.ts, "monthly")
modelname <- modelnames[chosen.model]
```

```{r monthly_fcast_Ominus, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "monthly")

# Scalings
fdf_for_plots <- fdf * reverse_adj[1:6] # We plot 6 months forward
```

```{r save_monthly_Ominus, echo = FALSE}
save_forecast(fdf, months = TRUE, modelname, "histories/monthly_Ominus.csv") # Check pffunctions.R
```

```{r, monthly_Ominus_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf_for_plots, freq = "monthly", monthly_real, "Ominus",  modelname, palette) # Check pffunctions.R
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for `r as.character(lubridate::month(today(), label = TRUE, abbr = FALSE))` `r lubridate::year(today())`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### O+
```{r monthly_model_selection_Oplus, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(monthly$Oplus, 49), 48)
series.ts <- ts(segment, start = decimal_date(beginning), frequency = 12)

chosen.model <- select_model(segment, beginning, series.ts, "monthly")
modelname <- modelnames[chosen.model]
```

```{r monthly_fcast_Oplus, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "monthly")

# Scalings
fdf_for_plots <- fdf * reverse_adj[1:6] # We plot 6 months forward
```

```{r save_monthly_Oplus, echo = FALSE}
save_forecast(fdf, months = TRUE, modelname, "histories/monthly_Oplus.csv") # Check pffunctions.R
```

```{r, monthly_Oplus_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf_for_plots, freq = "monthly", monthly_real, "Oplus",  modelname, palette) # Check pffunctions.R
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for `r as.character(lubridate::month(today(), label = TRUE, abbr = FALSE))` `r lubridate::year(today())`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### A-
```{r monthly_model_selection_Aminus, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(monthly$Aminus, 49), 48)
series.ts <- ts(segment, start = decimal_date(beginning), frequency = 12)

chosen.model <- select_model(segment, beginning, series.ts, "monthly")
modelname <- modelnames[chosen.model]
```

```{r monthly_fcast_Aminus, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "monthly")

# Scalings
fdf_for_plots <- fdf * reverse_adj[1:6] # We plot 6 months forward
```

```{r save_monthly_Aminus, echo = FALSE}
save_forecast(fdf, months = TRUE, modelname, "histories/monthly_Aminus.csv") # Check pffunctions.R
```

```{r, monthly_Aminus_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf_for_plots, freq = "monthly", monthly_real, "Aminus",  modelname, palette) # Check pffunctions.R
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for `r as.character(lubridate::month(today(), label = TRUE, abbr = FALSE))` `r lubridate::year(today())`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### A+
```{r monthly_model_selection_Aplus, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(monthly$Aplus, 49), 48)
series.ts <- ts(segment, start = decimal_date(beginning), frequency = 12)

chosen.model <- select_model(segment, beginning, series.ts, "monthly")
modelname <- modelnames[chosen.model]
```

```{r monthly_fcast_Aplus, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "monthly")

# Scalings
fdf_for_plots <- fdf * reverse_adj[1:6] # We plot 6 months forward
```

```{r save_monthly_Aplus, echo = FALSE}
save_forecast(fdf, months = TRUE, modelname, "histories/monthly_Aplus.csv") # Check pffunctions.R
```

```{r, monthly_Aplus_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf_for_plots, freq = "monthly", monthly_real, "Aplus",  modelname, palette) # Check pffunctions.R
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for `r as.character(lubridate::month(today(), label = TRUE, abbr = FALSE))` `r lubridate::year(today())`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### B-
```{r monthly_model_selection_Bminus, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(monthly$Bminus, 49), 48)
series.ts <- ts(segment, start = decimal_date(beginning), frequency = 12)

chosen.model <- select_model(segment, beginning, series.ts, "monthly")
modelname <- modelnames[chosen.model]
```

```{r monthly_fcast_Bminus, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "monthly")

# Scalings
fdf_for_plots <- fdf * reverse_adj[1:6] # We plot 6 months forward
```

```{r save_monthly_Bminus, echo = FALSE}
save_forecast(fdf, months = TRUE, modelname, "histories/monthly_Bminus.csv") # Check pffunctions.R
```

```{r, monthly_Bminus_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf_for_plots, freq = "monthly", monthly_real, "Bminus",  modelname, palette) # Check pffunctions.R
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for `r as.character(lubridate::month(today(), label = TRUE, abbr = FALSE))` `r lubridate::year(today())`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### B+
```{r monthly_model_selection_Bplus, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(monthly$Bplus, 49), 48)
series.ts <- ts(segment, start = decimal_date(beginning), frequency = 12)

chosen.model <- select_model(segment, beginning, series.ts, "monthly")
modelname <- modelnames[chosen.model]
```

```{r monthly_fcast_Bplus, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "monthly")

# Scalings
fdf_for_plots <- fdf * reverse_adj[1:6] # We plot 6 months forward
```

```{r save_monthly_Bplus, echo = FALSE}
save_forecast(fdf, months = TRUE, modelname, "histories/monthly_Bplus.csv") # Check pffunctions.R
```

```{r, monthly_Bplus_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf_for_plots, freq = "monthly", monthly_real, "Bplus",  modelname, palette) # Check pffunctions.R
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for `r as.character(lubridate::month(today(), label = TRUE, abbr = FALSE))` `r lubridate::year(today())`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### AB-
```{r monthly_model_selection_ABminus, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(monthly$ABminus, 49), 48)
series.ts <- ts(segment, start = decimal_date(beginning), frequency = 12)

chosen.model <- select_model(segment, beginning, series.ts, "monthly")
modelname <- modelnames[chosen.model]
```

```{r monthly_fcast_ABminus, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "monthly")

# Scalings
fdf_for_plots <- fdf * reverse_adj[1:6] # We plot 6 months forward
```

```{r save_monthly_ABminus, echo = FALSE}
save_forecast(fdf, months = TRUE, modelname, "histories/monthly_ABminus.csv") # Check pffunctions.R
```

```{r, monthly_ABminus_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf_for_plots, freq = "monthly", monthly_real, "ABminus",  modelname, palette) # Check pffunctions.R
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for `r as.character(lubridate::month(today(), label = TRUE, abbr = FALSE))` `r lubridate::year(today())`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### AB+
```{r monthly_model_selection_ABplus, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(monthly$ABplus, 49), 48)
series.ts <- ts(segment, start = decimal_date(beginning), frequency = 12)

chosen.model <- select_model(segment, beginning, series.ts, "monthly")
modelname <- modelnames[chosen.model]
```

```{r monthly_fcast_ABplus, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "monthly")

# Scalings
fdf_for_plots <- fdf * reverse_adj[1:6] # We plot 6 months forward
```

```{r save_monthly_ABplus, echo = FALSE}
save_forecast(fdf, months = TRUE, modelname, "histories/monthly_ABplus.csv") # Check pffunctions.R
```

```{r, monthly_ABplus_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf_for_plots, freq = "monthly", monthly_real, "ABplus",  modelname, palette) # Check pffunctions.R
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for `r as.character(lubridate::month(today(), label = TRUE, abbr = FALSE))` `r lubridate::year(today())`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### Platelets
```{r monthly_model_selection_plat, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(monthly$plat, 49), 48)
series.ts <- ts(segment, start = decimal_date(beginning), frequency = 12)

chosen.model <- select_model(segment, beginning, series.ts, "monthly")
modelname <- modelnames[chosen.model]
```

```{r monthly_fcast_plat, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "monthly")
fdf_for_tables <- chosen_forecast_extended(chosen.model, series.ts, freq = "monthly") # 2: EXTENDED

# 1 & 2: Scalings
fdf_for_plots <- fdf * reverse_adj[1:6] # We plot 6 months forward
fdf_pla_for_tables <- fdf_for_tables * reverse_adj # The tables need anything from 6 months to 23 months, so we just scale everything from the extended 
```

```{r save_monthly_plat, echo = FALSE}
save_forecast(fdf, months = TRUE, modelname, "histories/monthly_plat.csv")
```

```{r, monthly_pla_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf_for_plots, freq = "monthly", monthly_real, "plat", modelname, palette)
```
<style>
div.summary { background-color:#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for `r as.character(lubridate::month(last_month, label = TRUE, abbr = FALSE))` `r lubridate::year(last_month)`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` platelet units.

</div>
## Tables
```{r}
# First the following table
#      | realization x months ago ||    forecast for x months   |
# RED  | 6 | 5 | 4 | 3 | 2 | 1   || CURRENT | 2 | 3 | 4 | 5 | 6 |
# PLAT | 6 | 5 | 4 | 3 | 2 | 1   || CURRENT | 2 | 3 | 4 | 5 | 6 |

# This is not very pretty but the only way I know how at the moment
red_history <- c(monthly_real[monthly_real$date == last_month - months(6), ]$red,
                 monthly_real[monthly_real$date == last_month - months(5), ]$red,
                 monthly_real[monthly_real$date == last_month - months(4), ]$red,
                 monthly_real[monthly_real$date == last_month - months(3), ]$red,
                 monthly_real[monthly_real$date == last_month - months(2), ]$red,
                 monthly_real[monthly_real$date == last_month - months(1), ]$red)

plat_history <- c(monthly_real[monthly_real$date == last_month - months(6), ]$plat,
                  monthly_real[monthly_real$date == last_month - months(5), ]$plat,
                  monthly_real[monthly_real$date == last_month - months(4), ]$plat,
                  monthly_real[monthly_real$date == last_month - months(3), ]$plat,
                  monthly_real[monthly_real$date == last_month - months(2), ]$plat,
                  monthly_real[monthly_real$date == last_month - months(1), ]$plat)

# 6 months ahead (counting current month)
red_fcasts <- round(head(fdf_red_for_tables$fcast, 6), 0)
plat_fcasts <- round(head(fdf_pla_for_tables$fcast, 6), 0)

red_future <- c(red_fcasts[1], red_fcasts[2], red_fcasts[3],
                red_fcasts[4], red_fcasts[5], red_fcasts[6])
plat_future <- c(plat_fcasts[1], plat_fcasts[2], plat_fcasts[3],
                 plat_fcasts[4], plat_fcasts[5], plat_fcasts[6])

# Build dataframe for tabling
df1 <- rbind.data.frame(c(red_history, red_future), c(plat_history, plat_future))
rownames(df1) <- c("Red cells", "Platelets")
colnames(df1) <- c(paste0("history", "\n", month(last_month - months(6)), "/", year(last_month - months(6))), 
                   paste0("history", "\n", month(last_month - months(5)), "/", year(last_month - months(5))), 
                   paste0("history", "\n", month(last_month - months(4)), "/", year(last_month - months(4))),
                   paste0("history", "\n", month(last_month - months(3)), "/", year(last_month - months(3))),
                   paste0("history", "\n", month(last_month - months(2)), "/", year(last_month - months(2))), 
                   paste0("history", "\n", month(last_month - months(1)), "/", year(last_month - months(1))), 
                   paste0("forecast", "\n", month(last_month), "/", year(last_month)),
                   paste0("forecast", "\n", month(last_month + months(1)), "/", year(last_month + months(1))),
                   paste0("forecast", "\n", month(last_month + months(2)), "/", year(last_month + months(2))),
                   paste0("forecast", "\n", month(last_month + months(3)), "/", year(last_month + months(3))),
                   paste0("forecast", "\n", month(last_month + months(4)), "/", year(last_month + months(4))),
                   paste0("forecast", "\n", month(last_month + months(5)), "/", year(last_month + months(5))))

# Table it out
datatable(df1, rownames = TRUE, options = list(autoWidth = TRUE, 
                                               paging = FALSE, 
                                               searching = FALSE, 
                                               info = FALSE, 
                                               ordering = FALSE), 
          class = "cell-border")

# Then the yearly sums
#      | LAST | THIS | NEXT |
# RED  | real | fcast| fcast|
# PLAT | real | fcast| fcast|

# Sums
red_last <- sum(subset(monthly_real, format(as.Date(date), "%Y") == year(today()) - 1)$red)
red_this <- sum(subset(monthly_real, format(as.Date(date), "%Y") == year(today()))$red) + sum(fdf_red_for_tables[1:(13 - month(today())), ]$fcast)
red_next <- sum(fdf_red_for_tables[(14 - month(today())):(26 - month(today())), ]$fcast)
plat_last <- sum(subset(monthly_real, format(as.Date(date), "%Y") == year(today()) - 1)$plat)
plat_this <- sum(subset(monthly_real, format(as.Date(date), "%Y") == year(today()))$plat) + sum(fdf_pla_for_tables[1:(13 - month(today())), ]$fcast)
plat_next <- sum(fdf_pla_for_tables[(14 - month(today())):(26 - month(today())), ]$fcast)

df2 <- rbind.data.frame(c(red_last, red_this, red_next), c(plat_last, plat_this, plat_next))
rownames(df2) <- c("Red cells", "Platelets")
colnames(df2) <- c(paste0("history\n", year(today()) - 1),
                   paste0("forecast\n", year(today())),
                   paste0("forecast\n", year(today()) + 1))
# Table it out
datatable(df2, rownames = TRUE, options = list(autoWidth = TRUE, 
                                               paging = FALSE, 
                                               searching = FALSE, 
                                               info = FALSE, 
                                               ordering = FALSE), 
          class = "cell-border")
```

## 4 week forecast {.tabset .tabset-fade .tabset-pills}

### All red
```{r weekly_model_selection_red, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(weekly$red, 209), 208)
series.ts <- ts(segment, start = decimal_date(wbeginning), frequency = 52)

chosen.model <- select_model(segment, wbeginning, series.ts, "weekly")
```

```{r weekly_fcast_red, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "weekly")
```

```{r save_weekly_red, echo = FALSE}
save_forecast(fdf, months = FALSE, modelname, "histories/weekly_red.csv")
```

```{r, weekly_red_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf, freq = "weekly", history = weekly, "red", modelname, palette)
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for week `r week(last_month)` of `r lubridate::year(last_month)`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### O-
```{r weekly_model_selection_Ominus, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(weekly$Ominus, 209), 208)
series.ts <- ts(segment, start = decimal_date(wbeginning), frequency = 52)

chosen.model <- select_model(segment, wbeginning, series.ts, "weekly")
```

```{r weekly_fcast_Ominus, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "weekly")
```

```{r save_weekly_Ominus, echo = FALSE}
save_forecast(fdf, months = FALSE, modelname, "histories/weekly_Ominus.csv")
```

```{r, weekly_Ominus_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf, freq = "weekly", history = weekly, "Ominus", modelname, palette)
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for week `r week(last_month)` of `r lubridate::year(last_month)`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### O+
```{r weekly_model_selection_Oplus, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(weekly$Oplus, 209), 208)
series.ts <- ts(segment, start = decimal_date(wbeginning), frequency = 52)

chosen.model <- select_model(segment, wbeginning, series.ts, "weekly")
```

```{r weekly_fcast_Oplus, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "weekly")
```

```{r save_weekly_Oplus, echo = FALSE}
save_forecast(fdf, months = FALSE, modelname, "histories/weekly_Oplus.csv")
```

```{r, weekly_Oplus_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf, freq = "weekly", history = weekly, "Oplus", modelname, palette)
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for week `r week(last_month)` of `r lubridate::year(last_month)`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### A-
```{r weekly_model_selection_Aminus, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(weekly$Aminus, 209), 208)
series.ts <- ts(segment, start = decimal_date(wbeginning), frequency = 52)

chosen.model <- select_model(segment, wbeginning, series.ts, "weekly")
```

```{r weekly_fcast_Aminus, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "weekly")
```

```{r save_weekly_Aminus, echo = FALSE}
save_forecast(fdf, months = FALSE, modelname, "histories/weekly_Aminus.csv")
```

```{r, weekly_Aminus_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf, freq = "weekly", history = weekly, "Aminus", modelname, palette)
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for week `r week(last_month)` of `r lubridate::year(last_month)`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### A+
```{r weekly_model_selection_Aplus, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(weekly$Aplus, 209), 208)
series.ts <- ts(segment, start = decimal_date(wbeginning), frequency = 52)

chosen.model <- select_model(segment, wbeginning, series.ts, "weekly")
```

```{r weekly_fcast_Aplus, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "weekly")
```

```{r save_weekly_Aplus, echo = FALSE}
save_forecast(fdf, months = FALSE, modelname, "histories/weekly_Aplus.csv")
```

```{r, weekly_Aplus_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf, freq = "weekly", history = weekly, "Aplus", modelname, palette)
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for week `r week(last_month)` of `r lubridate::year(last_month)`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### B-
```{r weekly_model_selection_Bminus, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(weekly$Bminus, 209), 208)
series.ts <- ts(segment, start = decimal_date(wbeginning), frequency = 52)

chosen.model <- select_model(segment, wbeginning, series.ts, "weekly")
```

```{r weekly_fcast_Bminus, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "weekly")
```

```{r save_weekly_Bminus, echo = FALSE}
save_forecast(fdf, months = FALSE, modelname, "histories/weekly_Bminus.csv")
```

```{r, weekly_Bminus_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf, freq = "weekly", history = weekly, "Bminus", modelname, palette)
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for week `r week(last_month)` of `r lubridate::year(last_month)`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### B+
```{r weekly_model_selection_Bplus, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(weekly$Bplus, 209), 208)
series.ts <- ts(segment, start = decimal_date(wbeginning), frequency = 52)

chosen.model <- select_model(segment, wbeginning, series.ts, "weekly")
```

```{r weekly_fcast_Bplus, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "weekly")
```

```{r save_weekly_Bplus, echo = FALSE}
save_forecast(fdf, months = FALSE, modelname, "histories/weekly_Bplus.csv")
```

```{r, weekly_Bplus_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf, freq = "weekly", history = weekly, "Bplus", modelname, palette)
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for week `r week(last_month)` of `r lubridate::year(last_month)`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### AB-
```{r weekly_model_selection_ABminus, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(weekly$ABminus, 209), 208)
series.ts <- ts(segment, start = decimal_date(wbeginning), frequency = 52)

chosen.model <- select_model(segment, wbeginning, series.ts, "weekly")
```

```{r weekly_fcast_ABminus, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "weekly")
```

```{r save_weekly_ABminus, echo = FALSE}
save_forecast(fdf, months = FALSE, modelname, "histories/weekly_ABminus.csv")
```

```{r, weekly_ABminus_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf, freq = "weekly", history = weekly, "ABminus", modelname, palette)
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for week `r week(last_month)` of `r lubridate::year(last_month)`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### AB+
```{r weekly_model_selection_ABplus, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(weekly$ABplus, 209), 208)
series.ts <- ts(segment, start = decimal_date(wbeginning), frequency = 52)

chosen.model <- select_model(segment, wbeginning, series.ts, "weekly")
```

```{r weekly_fcast_ABplus, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "weekly")
```

```{r save_weekly_ABplus, echo = FALSE}
save_forecast(fdf, months = FALSE, modelname, "histories/weekly_ABplus.csv")
```

```{r, weekly_ABplus_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf, freq = "weekly", history = weekly, "ABplus", modelname, palette)
```

<style>
div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for week `r week(last_month)` of `r lubridate::year(last_month)`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

### Platelets
```{r weekly_model_selection_plat, echo = FALSE, results = FALSE}
# Define the series to be used
# We want to use 4 years of data. 3 years for the width of the rolling window and we'll let that run for a year.
segment <- head(tail(weekly$plat, 209), 208)
series.ts <- ts(segment, start = decimal_date(wbeginning), frequency = 52)

chosen.model <- select_model(segment, wbeginning, series.ts, "weekly")
```

```{r weekly_fcast_plat, echo = FALSE, results = FALSE}
# Now forecast with the chosen model
fdf <- chosen_forecast(chosen.model, series.ts, freq = "weekly")
```

```{r save_weekly_plat, echo = FALSE}
save_forecast(fdf, months = FALSE, modelname, "histories/weekly_plat.csv")
```

```{r, weekly_plat_fig, fig.align = "center", echo = FALSE}
draw_forecast(fdf, freq = "weekly", history = weekly, "plat", modelname, palette)
```

div.summary { background-color::#e6f0ff; border-radius: 5px; padding: 20px; font-size: 25px;}
</style>
<div class = "summary">

Forecast for week `r week(last_month)` of `r lubridate::year(last_month)`: `r format(round(head(fdf_for_plots$fcast, 1), 0))  # This is to round AND display only whole numbers.` blood bags.

</div>

## Monthly history {.tabset .tabset-fade .tabset-pills}

### All red

```{r red_history, fig.align = "center", echo = FALSE}
draw_history("histories/monthly_red.csv", monthly_real, freq = "monthly", "red", palette)
```

### O-
```{r Ominus_history, fig.align = "center", echo = FALSE}
draw_history("histories/monthly_Ominus.csv", monthly_real, freq = "monthly", "Ominus", palette)
```

### O+
```{r Oplus_history, fig.align = "center", echo = FALSE}
draw_history("histories/monthly_Oplus.csv", monthly_real, freq = "monthly", "Oplus", palette)
```

### A-
```{r Aminus_history, fig.align = "center", echo = FALSE}
draw_history("histories/monthly_Aminus.csv", monthly_real, freq = "monthly", "Aminus", palette)
```

### A+
```{r Aplus_history, fig.align = "center", echo = FALSE}
draw_history("histories/monthly_Aplus.csv", monthly_real, freq = "monthly", "Aplus", palette)
```

### B-
```{r Bminus_history, fig.align = "center", echo = FALSE}
draw_history("histories/monthly_Bminus.csv", monthly_real, freq = "monthly", "Bminus", palette)
```

### B+
```{r Bplus_history, fig.align = "center", echo = FALSE}
draw_history("histories/monthly_Bplus.csv", monthly_real, freq = "monthly", "Bplus", palette)
```

### AB-
```{r ABminus_history, fig.align = "center", echo = FALSE}
draw_history("histories/monthly_ABminus.csv", monthly_real, freq = "monthly", "ABminus", palette)
```

### AB+
```{r ABplus_history, fig.align = "center", echo = FALSE}
draw_history("histories/monthly_ABplus.csv", monthly_real, freq = "monthly", "ABplus", palette)
```

### Platelets
```{r plat_history, fig.align = "center", echo = FALSE}
draw_history("histories/monthly_plat.csv", monthly_real, freq = "monthly", "plat", palette)
```


## Weekly history {.tabset .tabset-fade .tabset-pills}

### All red
```{r red_weekly_history, fig.align = "center", echo = FALSE}
draw_history("histories/weekly_red.csv", weekly, freq = "weekly", "red", palette)
```

### O-
```{r Ominus_weekly_history, fig.align = "center", echo = FALSE}
draw_history("histories/weekly_Ominus.csv", weekly, freq = "weekly", "Ominus", palette)
```

### O+
```{r Oplus_weekly_history, fig.align = "center", echo = FALSE}
draw_history("histories/weekly_Oplus.csv", weekly, freq = "weekly", "Oplus", palette)
```

### A-
```{r Aminus_weekly_history, fig.align = "center", echo = FALSE}
draw_history("histories/weekly_Aminus.csv", weekly, freq = "weekly", "Aminus", palette)
```

### A+
```{r Aplus_weekly_history, fig.align = "center", echo = FALSE}
draw_history("histories/weekly_Aplus.csv", weekly, freq = "weekly", "Aplus", palette)
```

### B-
```{r Bminus_weekly_history, fig.align = "center", echo = FALSE}
draw_history("histories/weekly_Bminus.csv", weekly, freq = "weekly", "Bminus", palette)
```

### B+
```{r Bplus_weekly_history, fig.align = "center", echo = FALSE}
draw_history("histories/weekly_Bplus.csv", weekly, freq = "weekly", "Bplus", palette)
```

### AB-
```{r ABminus_weekly_history, fig.align = "center", echo = FALSE}
draw_history("histories/weekly_ABminus.csv", weekly, freq = "weekly", "ABminus", palette)
```

### AB+
```{r ABplus_weekly_history, fig.align = "center", echo = FALSE}
draw_history("histories/weekly_ABplus.csv", weekly, freq = "weekly", "ABplus", palette)
```

### Platelets
```{r plat_weekly_history, fig.align = "center", echo = FALSE}
draw_history("histories/weekly_plat.csv", weekly, freq = "weekly", "plat", palette)
```
