---
title: "Usage Lab: Red Cells (Ketju)"
output: github_document
---

```{r setup, echo=FALSE}
# Set working directory
knitr::opts_knit$set(root.dir = "/home/esa/production_forecasts") # Working on Ubuntu
# knitr::opts_knit$set(root.dir = "V:/production_forecasts") # Working home
```

```{r imports, message=FALSE}
library(forecast)
library(ggplot2)
library(gridExtra)
library(knitr)
library(readxl)
library(plyr)
library(lubridate)
source("src/evalhelp.R")
```

# Intro
Currently under development. In this notebook we study how to use hospital blood product usage data to create demand predictions.

## Create original datasets that should remain immutable throughout labbing
```{r message=FALSE}
# Load data
# All deliveries
deliv <- read_excel("./data/ketju_data.xlsx", sheet = "Ketju-punasolutoimitukset 2014-")[, c('Päivämäärä', 'Toimitukset')]
colnames(deliv) <- c("time", "deliveries")  # Change column names
deliv$time <- as.Date(deliv$time)


# Ketju usage 2014 -->
usage <- read.csv("./data/ketju_data.csv", header = TRUE, sep = ",", colClasses=c("NULL", "NULL", "NULL", "NULL", "NULL", "NULL", "NULL", "NULL", NA, "NULL", NA))
colnames(usage) <- c("time", "pcs")  # Change column names
usage$time <- mdy(usage$time)
usage <- arrange(usage, time)
usage <- aggregate(usage$pcs, by = list(usage$time), sum); colnames(usage) <- c("time", "pcs")
```

Check if the series have missing days
```{r}
date_range <- seq(min(deliv$time), max(deliv$time), by = 1)
date_range[!date_range %in% deliv$time]
```

The deliveries are missing 24 days. We will impute.

```{r}
deliv.imputed <- as.data.frame(rbind(deliv,
                                     c("2014-01-26", deliv$deliveries[deliv$time == "2014-01-19"]),
                                     c("2014-03-09", deliv$deliveries[deliv$time == "2014-03-02"]),
                                     c("2015-01-18", deliv$deliveries[deliv$time == "2015-01-11"]),
                                     c("2015-03-29", deliv$deliveries[deliv$time == "2015-03-22"]),
                                     c("2015-06-27", deliv$deliveries[deliv$time == "2015-06-20"]),
                                     c("2016-08-07", deliv$deliveries[deliv$time == "2016-07-31"]),
                                     c("2016-11-06", deliv$deliveries[deliv$time == "2016-10-30"]),
                                     c("2017-01-06", deliv$deliveries[deliv$time == "2016-12-30"]),
                                     c("2017-02-12", deliv$deliveries[deliv$time == "2017-02-05"]),
                                     c("2017-04-02", deliv$deliveries[deliv$time == "2017-03-26"]),
                                     c("2017-05-21", deliv$deliveries[deliv$time == "2017-05-14"]),
                                     c("2017-06-25", deliv$deliveries[deliv$time == "2017-06-18"]),
                                     c("2017-07-30", deliv$deliveries[deliv$time == "2017-07-23"]),
                                     c("2018-01-14", deliv$deliveries[deliv$time == "2018-01-07"]),
                                     c("2018-02-04", deliv$deliveries[deliv$time == "2018-01-28"]),
                                     c("2018-05-26", deliv$deliveries[deliv$time == "2018-05-19"]),
                                     c("2018-06-03", deliv$deliveries[deliv$time == "2018-05-27"]),
                                     c("2018-06-10", deliv$deliveries[deliv$time == "2018-06-04"]),
                                     c("2018-07-21", deliv$deliveries[deliv$time == "2018-07-14"]),
                                     c("2018-08-19", deliv$deliveries[deliv$time == "2018-08-12"]),
                                     c("2019-02-24", deliv$deliveries[deliv$time == "2019-02-17"]),
                                     c("2019-03-02", deliv$deliveries[deliv$time == "2019-02-23"]),
                                     c("2019-03-09", deliv$deliveries[deliv$time == "2019-03-03"]),
                                     c("2019-04-28", deliv$deliveries[deliv$time == "2019-04-21"]))); colnames(deliv.imputed) <- c("time", "deliveries")

deliv.imputed <- arrange(deliv.imputed, time)
```


```{r}
date_range <- seq(min(deliv.imputed$time), max(deliv.imputed$time), by = 1)
date_range[!date_range %in% deliv.imputed$time]
```


## Create time series
```{r}
ts.deliv <- ts(deliv.imputed$deliveries, start = 2014, frequency = 365)
ts.usage <- ts(usage$pcs, start = 2014, frequency = 365)
```


```{r}
Deliveries <- window(ts.deliv, start = 2019)
Usage <- window(ts.usage, start = 2019)
ggplot() + 
  autolayer(Deliveries) + 
  autolayer(Usage) + 
  ggtitle("Ketju-menekki vs. Ketju-toimitukset 2019") +
  ylab("Units") +
  xlab("Time") +
  scale_fill_discrete(name = "Series", labels = c("Deliveries", "Usage")) +
  theme(legend.position = "bottom")
```


```{r}
# Plot
usage.c <- ts(cumsum(usage$pcs), start = 2014, frequency = 365)
deliv.c <- ts(cumsum(deliv.imputed$deliveries), start = 2014, frequency = 365)
difference <- tail(cumsum(deliv.imputed$deliveries), 1) - tail(cumsum(usage$pcs), 1)
ggplot() + 
  autolayer(usage.c) + 
  autolayer(deliv.c) + 
  ylab("Units") +
  xlab("Time") +
  ggtitle(paste("Cumsum difference at end of series: ", difference))
```

There exists a 6% difference between deliveries and usage at the end of series. This is due to the fact that not all blood bags get used that get delivered!
